Toxic Code Snippets on Stack Overflow

### 2018-05-18 cloverflow-tse/cloverflow.tex
Revised until 2.2.1.

We call code snippets that are copied from software systems to online Q\&A
websites (such as Stack Overflow) and vice versa as ``online code clones''.
There are two directions in creating online code clones: (1)~code is cloned from
a software project to a Q\&A website as an example; or (2)~code is cloned from a
Q\&A website to a software project to obtain a functionality, perform a
particular task, or fixing a bug. % and (3)~code is transferred from one
% software project to another via a Q\&A website;
Similar to classic code clones, i.e.~clones between software systems, online
code clones can lead to license violations, bug propagation, introduction of
vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
difficult to locate and fix since the search space in online code corpora is
larger and no longer confined to a local repository.
Although this activity of online code cloning is well-known, there is only a few
empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
the on finding the origins of the clones.
We tackle this challenge of establishing existence of online code clones and
investigate how they occur in this study.

To have a deeper insight on online code clones, we surveyed 201 high-reputation
Stack Overflow answerers. The results of such a survey show that online code
cloning occurs on Stack Overflow. Stack Overflow answerers frequently clone code
from other locations, such as their personal projects, company projects, and
open source projects, to Stack Overflow as a solution or a complement to a
solution. The code cloning activity on Stack Overflow is obviously beneficial
considered the popularity of Stack Overflow and its influence on software
development~\cite{Ponzanelli2013,Ponzanelli2014,Park2014}. On the other hand,
there is also a downside caused by low quality, defective, and harmful code
snippets that are reused without an awareness by millions of users.

@@

Using the same analogy, in this study, we are interested in mining Stack
Overflow posts, detecting online code clones, and analysing the clones to reveal
``toxic code snippets''.

``Toxic code snippets mean code snippets that, after incorporating into software,
the cost of paying back the technical debt exceeds the value it generates in the long run.'' 
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
We chose to study toxic code snippets caused by outdated code and license-violating code snippets in
this study as the two problems are still under explored compared to code smells~\cite{Tufano2015} or vulnerabilities~\cite{Acar2016,Fischer2017}.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

The two toxic code snippets in our examples have been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times\footnote{The number of views
is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).} 
at
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet approximately every 5
days compared to almost every day for the second one. A quick web search shows
that the defective {\small{\texttt{humanReadableInt}}} method in the second
example already appears in approximately 500 projects on GitHub. Considering the
popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippet on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

@@

	\item \textbf{Awareness of Stack Overflow answerers and visitors to toxic code
	snippets:} We performed an online survey and collected answers from 201
highly-ranked Stack Overflow users and 87 Stack Overflow visitors. 
We found that the answerers cloned code snippets
from open source projects to Stack Overflow answers. While Stack Overflow
answerers are aware of their outdated code snippets, 19\% of the participants
rarely or never fix the code. 99\% of the answerers never include a software
license in their snippets and 69\% never check for licensing conflicts.
On the other hand, 66\% of the
Stack Overflow visitors experienced a problem from reusing Stack Overflow code snippets. 
They are generally not aware of the CC BY-SA 3.0 license, and more than
half of them never check for license compatibility when reusing Stack Overflow
code snippets.

	\item \textbf{A manual study of online code clones:} 
	To confirm the results in the surveys, we used
	two clone detection tools to discover 2,289 similar code snippet pairs between
	72,365 Java code snippets obtained from Stack Overflow's accepted answers and
	111 Java open source projects from the curated Qualitas
	corpus~\cite{QualitasCorpus}. We manually
	classified all of them.

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,289 online clones, at least 330 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 153 of them, we found evidence that they have been copied
	from a specific open source project. 100 of them we found to be outdated. %
	% and questionable for being reused.

@@

	\textit{2) How often are Stack Overflow
		visitors experience the outdated code and licensing conflicts when
		they copy an answer from Stack Overflow?}

@@

\subsection{Stack Overflow Developers' Survey} We support our motivation of
toxic code snippets on Stack Overflow and answer RQ1 by asking Stack
Overflow users to take an online survey. The survey was used for assessing awareness of
the developers on the two issues of outdated code and license-violating code
snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
anonymous and the participants could decide to leave at any time. 
We created two versions of the survey: \textbf{the answerer survey} and \textbf{the visitor survey}.
The answerer survey targeted the developers who were experienced Stack Overflow users
and were highly active in answering questions. On the other hand, the visitor survey
targeted the developers who searched for solutions and reused code from Stack Overflow answers.

@@

\textbf{The visitors' survey}
The survey consists of 16 questions: 9 Likert's
scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
open-ended questions. 
The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
The first four questions are mandatory while the other 12
questions will be shown to the participants based on their previous answers. 
The survey collects information about the participant's software development
experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
snippets, problems from Stack Overflow snippets, licensing of code on Stack
Overflow, and additional feedback. 
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of visiting Stack
Overflow for solving programming tasks at least once. The participants were
invited to take the survey via five channels: social media post (Facebook),
\textsf{blognone.com}, a popular technology news and media community in Thailand, the University of Molise in Italy where the third author
works, \texttt{comp.lang.java.programmer} group and the Software Engineering
Facebook page. 
The survey was open for participation for 2 months, 
from 25 July 2017 to 25 September 2017, before we collected and analysed
the responses.

\subsection{Empirical Study of Online Code Clones}
We support the motivation and the findings in the surveys by performing
an empirical study of online code clones between Stack Overflow
answers and 111 Java open source projects.
We designed the study in 6 phases as depicted in \Cref{fig:exp_framework} where
we build different data sets to answer RQ2 -- RQ5.

@@

Nevertheless, we have tried varying the minimum clone lines of 6, 10, and larger
than 10 for the two clone detection tools. The minimum clone size of 10 lines is
considered a standard setting for clone detection in large-scale data sets to
avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and
setter methods) in the analysis or the manual investigation
phase~\cite{Sajnani2016}. Choosing this size threshold larger than 10 could
possibly remove some non-trivial clones from the analysis, i.e.~create more
false negatives. On the other hand, decreasing the threshold to be lower than 10
lines will result in a larger number of clone candidate pairs to look at and a
higher chance of getting false positives. It is known that lowering the number
of minimum clone lines is harmful to precision. Moreover, the large number of
clone pairs will hinders the full manual validation of the clones and force us
to rely on sampling of clone pairs. We performed an analysis to confirm this. We
started by running the tools with minimum clone size of 10 lines and performing
the manual clone confirmation. Then, we compared the number of true clone pairs
detected if we increase or decrease the size.

\begin{figure}[H] \centering
	\includegraphics[width=0.8\linewidth]{boxplot_clone_size} 
	\caption{Size of online code clones.} 
	\label{fig:boxplotclonesize}
\end{figure}

Regarding increasing the minimum clone size to more than 10 lines (e.g. 15
lines), the result is as shown in
\Cref{fig:boxplotclonesize}. We found that the distribution of true clones; QS,
SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines. Increasing
the threshold to be higher than 10 would remove some of the trivial BP and IN
clone pairs which are not interesting for this study. However, it will also
remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.

Regarding decreasing the minimum clone size to be less than 10 lines, we reran
the two clone detection tools again using a minimum
clone size of 6 lines, another well-accepted minimum clone size in clone
benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs. 
With this large amount of clone
candidate pairs, it is not feasible to manually confirm all of the clones and we
must rely on sampling. This will result in weaker findings and
weaker conclusion. Thus, we decide pick the minimum clone size of 10 lines
to keep the balance between the number of non-trivial clone pairs and the
feasibility of manual clone investigation.
%We made sure that they 
%detected only non-trivial clones by increasing the minimum clone size to ten
%lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two people in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared. 
%and 607 (26\%)
%conflicts were discussed and resolved. 
There were 338 (15\%) conflicts between 
true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC).
The investigators looked at each conflicting pair together and
discussed until a consensus was made. 
Another 270 pairs (12\%) were
conflicts in the classification of
the true clone pairs. Among these pairs, 145 conflicts were caused by
one investigator being more careful than the other and being able to find evidence of 
copying while the other could not. Thus, resolving the conflicts lead to a better classification,
 i.e.~from UD to QS or EX.
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.

@@

		AC & Accidental similarity, false clones \\ 
		\bottomrule 
	\end{tabular}  %
	%}
\end{table}

\textbf{The online cloning classification patterns:} 
We studied the eight patterns of cloning from Kapser et
al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
evaluate its applicability to our study. 
We tried to classify 697 online clone pairs from
the reported clones in phase 1 
%Using the $S_D$ clone report,
%snippets were ranked according to (1)~clone pair frequency,
%(2)~popularity (i.e.~number of associated Qualitas projects),
%(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
%selected these four criteria so that we could cover the online clones
%from various aspects. We selected the top 10 from each ranking and
%obtained 34 unique Stack Overflow snippets. The snippets were
%associated with 697 clone pairs.
%\subsection{Defining Online Code Cloning Patterns}
using Kapser's cloning patterns. We found that 
% the
% clone pairs were categorised into either Customisation or Templating.
% Thus, 
Kapser's patterns are too broad for our study and a more suitable and
fine-grained classification scheme is needed. After a preliminary study, we
adopted one of Kapser's cloning patterns, \emph{boiler-plate code}, and defined
six new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP, IN, and
AC as presented in \Cref{tab:classification_scheme}. Pattern QS
(\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have
evidence of being copied from a Qualitas project to Stack Overflow. The evidence
of copying can be found in comments in the Qualitas source code or in the Stack
Overflow post's contents. Pattern SQ (\textbf{S}tack Overflow to
\textbf{Q}ualitas) is cloning, with evidence, in the opposite direction from
Stack Overflow to a Qualitas project. Pattern EX (\textbf{Ex}ternal Sources) is
cloning that has evidence of copying from a single or multiple external sources
to Stack Overflow, and possibly also to a Qualitas project.  Pattern UD
(\textbf{U}nknown \textbf{D}irection) is cloning that creates identical or
highly similar clones between Qualitas and Stack Overflow but where we could not
find any attribution of copying. Pattern BP (\textbf{B}oiler-\textbf{P}late)
represents clones containing boiler-plate. We define three cases of boiler-plate
code and use in our classification as shown in \Cref{tab:boiler-plate_code}. Our
definition is specific to Java and more suitable to our study than the general
definition in Kapser's~\cite{Kapser2008}.
%of {\small\verb|equals()|} methods,
%getters/setters, well-known code patterns such as deleting a file
%or implementing a {\small{\texttt{toString}} method,
% or IDE-generated code such as GUI components. 
 Pattern
IN (\textbf{In}heritance/Interface) is cloning by inheritance of the
same super class or implementation of the same interface. These two
activities usually result in similar overriding methods. The last
pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents
accidentally similar clone pairs. These are mainly false positive
clones from the clone detectors such as similar
{\small\texttt{try-catch}} statements.

@@

The classification of the filtered online clone pairs followed the steps
depicted in \Cref{fig:classification_process}. First, we look at a pair of clone
fragments to see their similarity. If they are accidentally similar clones after
code normalisation or false positive clones from the clone detection tools, we
classify the pair into \textbf{AC}. If the two fragments are boiler-plate code,
the pair is classified into \textbf{BP}. If they implement the same interface or
inherited the same class and share similar overriding methods, the pair is
classified into \textbf{IN}. If the pair is not \textbf{BP}, \textbf{IN}, or
\textbf{AC}, we start a detailed investigation. We check the corresponding Stack
Overflow post, read through it carefully and look for any evidence mentioning
code copying. If evidence of copying has been found from a Qualitas project, the
pair is classified in \textbf{QS}. In several occasions, we used extra
information such as questions' contents, name of posters, and tags to gain a
better understanding. On the other hand, if the source code from the Qualitas
project mentions copying from Stack Overflow, the pair is classified into
\textbf{SQ}. If there is evidence of copying from an external source instead of
a Qualitas projects, the pair is classified into \textbf{EX}. Lastly, if there
is no evidence of copying in any direction but the clone fragments are highly
similar, we classify them into \textbf{UD}.

@@

We found that although the answerer have been notified of outdated code in their
answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
of the answers). Only 3 participants reported that they were notified in more
than 60\% of their answers. This notification to the answerer can be done by
posting comments for that answer on Stack Overflow. For example, the answerer of
the Stack Overflow question no.~10924648 posted a comment on his own answer
saying that the answer is specifically for Spring 3.1. Moroever, another user
posted a comment on the answer of the post no.~801935 that the code snippet is
not of high quality and suggested an alternative in another post.

@@

\vspace{0.25cm}
\textit{Do Stack Overflow
	visitors experience outdated code and check for licensing conflicts when
	they copy and reuse answer from Stack Overflow?}
\vspace{0.25cm}

@@

Lastly, during the manual investigation of 2,289 clone pairs, we identified 226 pairs
as being accidental clones (AC), i.e.~false positives. After removing
them, the set still contains 2,076 true positive clone pairs between 443 Stack
Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
true positive clone pairs is 53.89\%.

@@

\begin{table*}
	\centering
	\caption{Classifications of online clone pairs.}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrrrrrrrr}
		\toprule
		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
		\midrule
		Before consolidation & 247 & 1 & 197 & 107 & 1,495 & 16 & 226 & 2,289 \\
		After consolidation & 153 & 1 & 109 & 65 & 216 & 9 & 53 & 606 \\
		\bottomrule
	\end{tabular} 
	%}
\end{table*}

@@

\textbf{AC: Accidental Clones.} There were 226 accidental clone
pairs, 53 after consolidation. Mainly, they are false positive clones caused by code
normalisation and false type-3 clones from SourcererCC. 
Examples of the AC clone instances include {\small\texttt{finally}} or
{\small\texttt{try-catch}} clauses that were accidentally the same due
to their very small sizes, and similar {\small\texttt{switch-case}}
statements.

>>>>

We call code snippets that are copied from software systems to online Q\&A
websites (such as Stack Overflow) and vice versa as ``online code clones''.
There are two directions in creating online code clones: (1)~code is cloned from
a software project to a Q\&A website as an example; or (2)~code is cloned from a
Q\&A website to a software project to obtain a functionality, perform a
particular task, or fixing a bug. % and (3)~code is transferred from one
% software project to another via a Q\&A website;
Similar to classic code clones, i.e.~clones between software systems, online
code clones can lead to license violations, bug propagation, introduction of
vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
difficult to locate and fix since the search space in online code corpora is
larger and no longer confined to a local repository.

To have a deeper insight on online code clones, we surveyed 201 high-reputation
Stack Overflow answerers. The results of such a survey show that online code
cloning occurs on Stack Overflow. Stack Overflow answerers frequently clone code
from other locations, such as their personal projects, company projects, and
open source projects, to Stack Overflow as a solution or a complement to a
solution. The code cloning activity on Stack Overflow is obviously beneficial
considered the popularity of Stack Overflow and its influence on software
development~\cite{Ponzanelli2013,Ponzanelli2014,Park2014}. On the other hand,
there is also a downside caused by low quality, defective, and harmful code
snippets that are reused without an awareness by millions of users~\cite{Zhang2018,Acar2016,Fischer2017}.

@@

Although this activity of online code cloning is well-known, there is only a few
empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
on finding the origins of the clones on Q\&A websites.
In this study, we tackle this challenge of establishing existence of online code 
clones on Stack Overflow, investigate how they occur, and study the potential
effects to software reusing them.
%Using the same analogy, in this study, we are interested in 
Therefore, we mine Stack Overflow posts, detected online code clones, and analysed the clones to reveal
``toxic code snippets''.

Toxic code snippets mean code snippets that, after incorporating into software,
the cost of paying back the technical debt exceeds the value it generates in the long run.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
as these two problems are still under explored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

The two toxic code snippets in our examples have been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times\footnote{The number of views
is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).} 
at
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet approximately every 5
days compared to almost every day for the second one. 
%A quick web search shows
%that the defective {\small{\texttt{humanReadableInt}}} method in the second
%example already appears in approximately 500 projects on GitHub. 
Considering the popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippet on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

@@

	\item \textbf{Awareness of Stack Overflow answerers and visitors to toxic code
	snippets:} We performed an online survey and collected answers from 201
highly-ranked Stack Overflow users and 87 Stack Overflow visitors. 
We found that the answerers cloned code snippets
from open source projects to Stack Overflow answers. While Stack Overflow
answerers are aware of their outdated code snippets, 19\% of the participants
rarely or never fix the code. 99\% of the answerers never include a software
license in their snippets and 69\% never check for licensing conflicts.
On the other hand, 66\% of the
Stack Overflow visitors experienced problems from reusing Stack Overflow code snippets, including outdated code. 
They are generally not aware of the CC BY-SA 3.0 license, and more than
half of them never check for license compatibility when reusing Stack Overflow
code snippets.

	\item \textbf{A manual study of online code clones:} 
	To empirically confirm the findings from the surveys, we used
	two clone detection tools to discover 2,289 similar code snippet pairs between
	72,365 Java code snippets obtained from Stack Overflow's accepted answers and
	111 Java open source projects from the curated Qualitas
	corpus~\cite{QualitasCorpus}. We manually
	classified all of them.

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,289 online clones, at least 328 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 153 of them, we found evidence that they have been copied
	from a specific open source project. 100 of them we found to be outdated. %
	% and questionable for being reused.

@@

	\textit{2) How often do Stack Overflow
		visitors experience the outdated code and licensing conflicts when
		they reuse code in an answer from Stack Overflow?}

@@

\subsection{Stack Overflow Developers' Survey} We support our motivation of
toxic code snippets on Stack Overflow and answer RQ1 by asking Stack
Overflow users to take an online survey. The survey was used for assessing awareness of
the developers on the two issues of outdated code and license-violating code
snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
anonymous and the participants could decide to leave at any time. 
We created two versions of the survey: \textbf{the answerer survey} and \textbf{the visitor survey}.
The answerer survey targeted the developers who were experienced Stack Overflow users
and were highly active in answering questions. The visitor survey
targeted the developers who searched for solutions and reused code from Stack Overflow answers.

@@

\textbf{The visitors' survey}
The survey consists of 16 questions: 9 Likert's
scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
open-ended questions. 
The first four questions are mandatory while the other 12
questions will be shown to the participants based on their previous answers. 
The survey collects information about the participant's software development
experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
snippets, problems from Stack Overflow snippets, licensing of code on Stack
Overflow, and additional feedback. 
The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of visiting Stack
Overflow for solving programming tasks at least once. The participants were
invited to take the survey via five channels: social media post (Facebook),
\textsf{blognone.com}, a popular technology news and media community in Thailand, the University of Molise in Italy where the third author
works, \texttt{comp.lang.java.programmer} group and the Software Engineering
Facebook page. 
The survey was open for participation for 2 months 
from 25 July 2017 to 25 September 2017.

\subsection{Empirical Study of Online Code Clones}
We support the motivation and the findings in the surveys by performing
an empirical study of online code clones between Stack Overflow
answers and 111 Java open source projects.
We designed the study in 6 phases as depicted in \Cref{fig:exp_framework} where
we build different data sets to answer RQ2 to RQ5.

@@

Nevertheless, we investigated a crucial parameter setting for clone detection: the minimum clone size threshold.
Choosing a large clone size threshold can reduce the number of false clones reported,
while at the same time creates some false negatives, i.e.~missing some of the true clones.
On the other hand, setting a low threshold results in a larger number of clone
candidate pairs to look at and a higher chance of getting false positives.
It is known that lowering the number of minimum clone lines is harmful to precision.
Moreover, the large number of clone pairs will hinders the full manual
validation of the clones and one needs to rely on sampling of clone pairs.
We started our investigation by using a minimum clone
size of 6 lines, a well-accepted minimum clone size in clone
benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
SourcererCC reported 7,752 clone candidate pairs. We randomly sampled 382 pairs
from the merged set of 74,148 clone pairs and the first author investigated them. This was
a statistical significant sample with a 95\% confidence level and $\pm 5\%$ confidence interval.
We found 322 trivial clone pairs including \texttt{equals}, \texttt{hashCode}, or getters/setters;
26 non clone pairs, and 34 non-trivial clone pairs.
We then increased the minimum clone size to 10 lines, another well-established 
minimum clone size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from Simian and
1,678 clone pairs from SourcererCC. We randomly sampled and manually checked the same amount of 382 pairs
from the merged set of 2,289 clone pairs.
We found 251 trivial clone pairs, 40 non-clone pairs, and 91 non-trivial clone pairs.

The findings from the two samples show that selecting the minimum of 6 lines generated
a large number of clones (74,148 pairs) with more trivial clone pairs, which we were not interesting for this study, 
and fewer non-trivial pairs compared to the minimum of 10 lines.
%To put it another way, lowering the number of clone lines is harmful to precision.
Moreover, the amount of 2,289 clone pairs using minimum of 10 clone lines 
was feasible for manual investigation in the next phase.
Increasing the minimum clone size further will result in a smaller clone subset
but may also remove some of the true clone pairs (generating false negatives).
Thus, we selected the minimum clone size of 10 lines for both Simian and SourcererCC.

%The minimum clone size of 10 lines is
%considered a standard setting for clone detection in large-scale data sets to
%avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and
%setter methods) in the analysis or the manual investigation phase~\cite{Sajnani2016}.  
%We
% performed an analysis to confirm this.
%\begin{figure} 
%	\centering
%	\includegraphics[width=\linewidth]{boxplot_clone_size_combined} 
%	\caption{Size of online code clones.} 
%	\label{fig:boxplotclonesize}
%\end{figure}

%The result is as shown in
%\Cref{fig:boxplotclonesize}. We found that the distribution of the manually
%confirmed true clones 
%mainly cover the size from about 10 to 20 lines. Increasing
%the threshold to be higher than 10 would remove some of the
%true clone pairs.
%
%Regarding decreasing the minimum clone size to be less than 10 lines, we reran
%the two clone detection tools again using a minimum
%clone size of 6 lines, another well-accepted minimum clone size in clone
%benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
%SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs. 
%With this large amount of clone
%candidate pairs, it is not feasible to manually confirm all of the clones and we
%must rely on sampling. This will result in weaker findings and
%weaker conclusion. Thus, we decide pick the minimum clone size of 10 lines
%to keep the balance between the number of non-trivial clone pairs and the
%feasibility of manual clone investigation.
%We made sure that they 
%detected only non-trivial clones by increasing the minimum clone size to ten
%lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two people in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared. 
%and 607 (26\%)
%conflicts were discussed and resolved. 
There were 338 (15\%) conflicts between 
true and false clones (QS, SQ, EX, UD, BP, IN vs.~NC).
The investigators looked at each conflicting pair together and
discussed until a consensus was made. 
Another 270 pairs (12\%) were
conflicts in the classification of
the true clone pairs. Among these pairs, 145 conflicts were caused by
one investigator being more careful than the other and being able to find evidence of 
copying while the other could not. Thus, resolving the conflicts lead to a better classification,
 i.e.~from UD to QS or EX.
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.

@@

		NC & Not clones \\ 
		\bottomrule 
	\end{tabular}  %
	%}
\end{table}

\textbf{The online cloning classification patterns:} 
We studied the eight patterns of cloning from Kapser et
al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
evaluate its applicability to our study. 
We tried to classify 697 online clone pairs from
the reported clones in phase 1 
%Using the $S_D$ clone report,
%snippets were ranked according to (1)~clone pair frequency,
%(2)~popularity (i.e.~number of associated Qualitas projects),
%(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
%selected these four criteria so that we could cover the online clones
%from various aspects. We selected the top 10 from each ranking and
%obtained 34 unique Stack Overflow snippets. The snippets were
%associated with 697 clone pairs.
%\subsection{Defining Online Code Cloning Patterns}
using Kapser's cloning patterns. We found that 
% the
% clone pairs were categorised into either Customisation or Templating.
% Thus, 
Kapser's patterns are too broad for our study and a more suitable and
fine-grained classification scheme is needed. After a preliminary study, we
adopted one of Kapser's cloning patterns, \emph{boiler-plate code}, and defined
six new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP, IN, and
NC as presented in \Cref{tab:classification_scheme}. Pattern QS
(\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have
evidence of being copied from a Qualitas project to Stack Overflow. The evidence
of copying can be found in comments in the Qualitas source code or in the Stack
Overflow post's contents. Pattern SQ (\textbf{S}tack Overflow to
\textbf{Q}ualitas) is cloning, with evidence, in the opposite direction from
Stack Overflow to a Qualitas project. Pattern EX (\textbf{Ex}ternal Sources) is
cloning that has evidence of copying from a single or multiple external sources
to Stack Overflow, and possibly also to a Qualitas project.  Pattern UD
(\textbf{U}nknown \textbf{D}irection) is cloning that creates identical or
highly similar clones between Qualitas and Stack Overflow but where we could not
find any attribution of copying. Pattern BP (\textbf{B}oiler-\textbf{P}late)
represents clones containing boiler-plate. We define three cases of boiler-plate
code and use in our classification as shown in \Cref{tab:boiler-plate_code}. Our
definition is specific to Java and more suitable to our study than the general
definition in Kapser's~\cite{Kapser2008}.
%of {\small\verb|equals()|} methods,
%getters/setters, well-known code patterns such as deleting a file
%or implementing a {\small{\texttt{toString}} method,
% or IDE-generated code such as GUI components. 
 Pattern
IN (\textbf{In}heritance/Interface) is cloning by inheritance of the
same super class or implementation of the same interface. These two
activities usually result in similar overriding methods. The last
pattern, NC (\textbf{N}ot \textbf{C}lones), represents
false clone pairs. These are mainly false positive
clones from the clone detectors such as similar
{\small\texttt{try-catch}} statements.

@@

The classification of the filtered online clone pairs followed the steps
depicted in \Cref{fig:classification_process}. First, we look at a pair of clone
fragments to see their similarity. If they are accidentally similar clones after
code normalisation or false positive clones from the clone detection tools, we
classify the pair into \textbf{NC}. If the two fragments are boiler-plate code,
the pair is classified into \textbf{BP}. If they implement the same interface or
inherited the same class and share similar overriding methods, the pair is
classified into \textbf{IN}. If the pair is not \textbf{BP}, \textbf{IN}, or
\textbf{NC}, we start a detailed investigation. We check the corresponding Stack
Overflow post, read through it carefully and look for any evidence mentioning
code copying. If evidence of copying has been found from a Qualitas project, the
pair is classified in \textbf{QS}. In several occasions, we used extra
information such as questions' contents, name of posters, and tags to gain a
better understanding. On the other hand, if the source code from the Qualitas
project mentions copying from Stack Overflow, the pair is classified into
\textbf{SQ}. If there is evidence of copying from an external source instead of
a Qualitas projects, the pair is classified into \textbf{EX}. Lastly, if there
is no evidence of copying in any direction but the clone fragments are highly
similar, we classify them into \textbf{UD}.

@@

We found that although the answerer have been notified of outdated code in their
answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
of the answers). Only 3 participants reported that they were notified in more
than 60\% of their answers. This notification to the answerer can be done by
posting comments below the answer on Stack Overflow. For example, the answerer of
the Stack Overflow question no.~10924648 posted a comment on his own answer
saying that the answer is specifically for Spring 3.1. Moroever, another user
posted a comment on the answer of the post no.~801935 that the code snippet is
not of high quality and suggested an alternative in another post.

@@

\vspace{0.25cm}
\textit{How often do Stack Overflow
	visitors experience the outdated code and licensing conflicts when
	they reuse code in an answer from Stack Overflow?}
\vspace{0.25cm}

@@

Lastly, during the manual investigation of 2,289 clone pairs, we identified 226 pairs
as being accidental clones (NC), i.e.~false positives. After removing
them, the set still contains 2,076 true positive clone pairs between 443 Stack
Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
true positive clone pairs is 53.89\%.

@@

\begin{table*}
	\centering
	\caption{Classifications of online clone pairs.}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrrrrrrrr}
		\toprule
		Set & QS & SQ & EX & UD & BP & IN & NC & Total \\ 
		\midrule
		Before consolidation & 247 & 1 & 197 & 107 & 1,495 & 16 & 226 & 2,289 \\
		After consolidation & 153 & 1 & 109 & 65 & 216 & 9 & 53 & 606 \\
		\bottomrule
	\end{tabular} 
	%}
\end{table*}

@@

\textbf{NC: Not Clones.} There were 226 non-clone
pairs, 53 after consolidation. Mainly, they are false positive clones caused by code
normalisation and false type-3 clones from SourcererCC. 
Examples of the NC clone instances include {\small\texttt{finally}} or
{\small\texttt{try-catch}} clauses that were accidentally the same due
to their very small sizes, and similar {\small\texttt{switch-case}}
statements.
